Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-30 introduction.tex
Minor edits to introduction.

% Programmable hardware monitors
These run-time monitors introduce performance, power, and energy overheads.
% Implementing run-time monitoring in software using binary instrumentation or
% other similar methods has been shown to introduce high overheads. For example,
% dynamic information flow tracking (DIFT) implemented in software suffers a 3.6x
% slowdown \cite{lift-micro06}. 
Implementing monitors in dedicated hardware has shown to have very small
performance impacts. For example, a dedicated hardware implementation of
dynamic information flow tracking (DIFT) shows performance
overheads of only 1.1\% \cite{dift-asplos04}. However, fixed hardware loses
the programmability of software, and cannot be updated or changed. It also
requires for monitors to be chosen and implemented at hardware design time.
Recent studies \cite{lba-isca08} have proposed using parallel cores in a
multi-core system to perform monitoring. This allows monitoring to be done
using parallel hardware while having the flexibility and programmability of
software. However, due to the multiple cycles it may take for software to
monitor an instruction, the overheads can easily increase execution time
several fold.

% Two optimizations
In this paper, we present a hardware architecture that uses dynamic dataflow
tracking in order to reduce the overheads of programmable parallel monitoring.
This dataflow tracking engine is used to filter out unnecessary monitoring and
enable partial monitoring.

>>>>

% Programmable hardware monitors
These run-time monitors introduce performance, power, and energy overheads.
% Implementing run-time monitoring in software using binary instrumentation or
% other similar methods has been shown to introduce high overheads. For example,
% dynamic information flow tracking (DIFT) implemented in software suffers a 3.6x
% slowdown \cite{lift-micro06}. 
Implementing monitors in dedicated hardware has been shown to have small
performance impacts. For example, a dedicated hardware implementation of
dynamic information flow tracking (DIFT) shows performance
overheads of only 1.1\% \cite{dift-asplos04}. However, fixed hardware loses
the programmability of software, and cannot be updated or changed. It 
requires for monitors to be chosen and implemented at hardware design time.
Recent studies \cite{lba-isca08} have proposed using parallel cores in a
multi-core system to perform monitoring. This allows monitoring to be done
using parallel hardware while having the flexibility and programmability of
software. However, due to the multiple cycles it may take for software to
monitor an instruction, the overheads can easily increase execution time
several fold.
% Two optimizations
In this paper, we present a hardware architecture that uses dynamic dataflow
tracking in order to reduce the overheads of programmable parallel monitoring
by filtering out unnecessary monitoring operations and by enabling partial
monitoring.
